Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-10-24 batchdedup/arch.tex
differentiated stage 4a and 4b in architecture

In the final Stage of our algorithm, Stage 4, All duplicate references,
including dup-with-new blocks, are returned to the requesters from the index
holders and the snapshot
recipes are updated with those pointers.

>>>>

In the final Stage of our algorithm, Stage 4, All duplicate references,
including dup-with-new blocks, are returned to the requesters from the index
holders in 4a, And in 4b the snapshot recipes are updated with those pointers.
